Template for GTEx example on cluster

### 2017-10-06 analysis/GTEXzscoreTemplate.Rmd
Files commited by wflow_commit.

```{r}
gt10 = readRDS('../data/GTExdata/SFAres/sfaTYK_10.rds')

par(mfrow = c(2,3),mar=c(5.1,4.1,4.1,2.1)-1.9)
for(k in 1:10){
  barplot(gt10$L[,k],main = paste("factor",k))
}
```

>>>>

If you would like to use `t(Y)` you should use `-vn` in the `sfa` command line in order to get $(\hat{\sigma}_1^2,\cdots,\hat{\sigma}_j^2,\cdots)$ is a `16069` vector

you need add `-mg` to get the mean vector with length of 44

```{r}
gt10 = readRDS('../data/GTExdata/SFAres/sfaTK_10m.rds')
mu = sapply(seq(1:44),function(x){gt10$mu[[x]]})
par(mfrow = c(2,3),mar=c(5.1,4.1,4.1,2.1)-1.9)
barplot(mu,main = "mean vector")
for(k in 1:10){
  barplot(gt10$LF$L[,k],main = paste("factor",k))
}
```
